A data-intensive assessment of the species-abundance distribution.

### 2015-04-01 defense_pres.tex
Expands introduction, simplifies signal and noise slides.

\section{Introduction}
\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach to studying ecological patterns and processes.\\
\begin{itemize}
\item Data intensive.
\item Large scales.
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\item Search for generality.
\end{itemize}
\end{frame}

@@

\subsection{Signal and Noise}
\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.jpg}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.jpg}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.28]{../Miscellaneous/Pictures/Maps/TheMaps.jpg}
\end{center}
\end{frame}

\subsection{Criticisms of macroecology}
\begin{frame}[t]
\frametitle{Macroecology}
Criticisms of macroecology\\
\begin{itemize}
\item North American terrestrial bias.
\item Lack of identification of pattern generating mechanisms.
\end{itemize}
\end{frame}

>>>>

\section{Introduction}
\subsection{Commonness & rarity}
\begin{frame}[t]
\frametitle{Commonness \& rarity}
"Who can explain why one species ranges widely, and is very numerous, and why another allied species has a narrow range and is rare?  Yet these relations are of the highest important, for they determine the present welfare and, as I believe, the future success and modification of every inhabitant of this world."

Darwin, 1859.

\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
\end{frame}

\begin{frame}
Species abundance distribution
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\item Exhibits a hollow curve distribution.
\end{itemize}
\note{
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach to studying ecological patterns and processes.\\
\begin{itemize}
\item Data intensive.
\item Large scales.
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\item Search for generality.
\end{itemize}
\end{frame}

@@

\subsection{Challenges of macroecology}
\begin{frame}[t]
\frametitle{Macroecology}
Challenges of macroecology\\
\begin{itemize}
\item Studies performed with a limited number of large datasets.
\item Lack of identification of pattern generating mechanisms.
\end{itemize}
\note{
Taxonomic and ecosystem limitations in datasets, e.g.North American terrestrial bias.}
\end{frame}

\subsection{Signal and Noise}
\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.4]{./sad-data/chapter3/SignalNoise.png}
\end{center}
\end{frame}
